Target Readability in Interpersonal Accuracy

### 2022-05-16 manuscript.Rmd
finish intro

---
title: "Accuracy of Thoughts, Affect, and Personality impressions"
author: "Murat Kezer"
output: 
    html_document:
      theme: cerulean
      code_download: TRUE
      toc: TRUE
      toc_float:
        collapsed: FALSE
      toc_depth: 3
      code_folding: hide
---

@@

# Method
## Participants

@@

>>>>

---
title: "Target Readability in Interpersonal Accuracy"
author: "Murat Kezer"
output: 
    html_document:
      theme: cerulean
      code_download: TRUE
      toc: TRUE
      toc_float:
        collapsed: FALSE
      toc_depth: 3
      code_folding: hide
---

@@

  Common sense suggests that navigating our complex social environment requires at least a basic competency at making accurate judgments of others as well as making oneself readable to others. However, one common theme across domains of interpersonal perception research has been a disproportionate focus on perceivers, emphasizing traits, motivations, and biases that allow perceivers to accurately understand targets (for reviews
see Davis & Kraus, 1997; Hall & Bernieri, 2001). This one-sided focus has come at the expense of understanding the role targets play in these processes. Making the inevitable comparison to reading a passage of text, we know much more about the reader than we do about the book. The imbalance is striking given that interpersonal perception is inherently dyadic – a perceiver cannot make a judgment without a target person to judge. The overarching goal of this project is to address this imbalance and explore what makes for more or less “readable” targets.

  According to Funder’s (1995) Realistic Accuracy Model, accurate interpersonal perceptions can be facilitated by good judges, but also by good targets.Funder further proposed that accurate perceptions are a product of a series of stages. A target must emit some relevant behavior that is made available to the perceiver. The perceiver must then detect these cues and correctly utilize them to make a judgment. Note that RAM is not a general process model of how all interpersonal judgments are formed, but rather a description of how accurate judgments are formed. The target’s direct role in
this process will be most important in the first two stages (relevance and availability). Characteristics that make targets more likely to emit relevant cues and enhance the availability of those cues are likely to be correlated with readability. The present study focuses on three groups of predictors of target readability: Expressivity, social-threat sensitivity and psychological adjustment.

  Even though studies suggest that the good target seems to be a more plausible determinate of interpersonal accuracy than the good judge, we still know much less about which targets are more readable than others and whether
or not target readability is a general trait or if it is instead specific to different types of judgments. The goal of this project is to address this imbalance. Because looking for more or less readable targets presumes individual differences in readability, Aim 1 is to examine how variance in interpersonal accuracy is distributed across levels (i.e., how variance associated with differences among targets compares to variance associated with differences among perceivers). Aim 2 is to examine whether target readability correlates across measures (e.g., whether a target whose personality traits are easy to read also has affect that is easy read) by using multiple accuracy measures that represent a range of interpersonal judgments. To capture a more complete picture of the complexity of interpersonal processes, the dimensions targets were judged on ranged from stable (i.e., personality traits) to dynamic (i.e., continuous affect and discrete thoughts that potentially change moment by moment). And finally Aim 3 is to explore the individual differences (assessing the constructs described above) that may correlate with target readability and look for patterns of interrelations across outcome measures.

  In order to test these research aims, participants were videotaped interacting with a partner during brief “getting-acquainted” conversations using a round-robin design where each person served as perceiver and target in multiple interactions. After interacting, people rated their partner’s personality traits, and dynamically changing affect and thoughts. In order to assess accuracy, each partner made parallel ratings about their own traits, affect, and thoughts. Measures of expressivity, social-threat sensitivity,
and psychological adjustment were collected at a later time point from the participants as well as informants in order to examine whether these variables were related to target readability on traits, affect, and thoughts.

# Method
## Participants
Undergraduates from the University of Oregon participated in this study in
exchange for course credit. In total, 53 groups of four participated in this study, which resulted in a total of 212 participants (63.7% women; Mage = 20.17, SDage = 2.99; 68.4% Caucasian, 11.8% Asian, 5.7% Black, 5.7% Hispanic, 8.4% other or missing). Participants were asked not to sign up for the study with friends so the partners were generally unacquainted.

@@

# Discussion

# Author Note
"This project was completed by Dr. Karyn Lewis in 2014. Introduction and method sections are mostly copied from Dr. Lewis' dissertation, which were adapted and edited for the current project."
